Incentivizing Exploration by Heterogeneous Users

### 2018-06-05 Lemmas.tex
checked and edited lemma 7

\begin{rlemma}{Lemma}{\ref{lem:no-incentives}}
Fix an arm $i$.
Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
time when arm $i$ is pulled for the \Kth{s} time.
Under \AccEU{\tau_s}{\frac{p}{4\Diam d \TieDensity}},
this pull of arm $i$ is not incentivized.
\end{rlemma}

\begin{proof}
By Lemma~\ref{lem:right-choice},
under the event \AccEU{\tau_s}{\frac{\MinProb}{4\Diam d \TieDensity}},
all agent types \AgV with
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
> \frac{\MinProb}{2\TieDensity}$
will pull their best arm \Best{\AgV}.

By Assmption~\ref{A1},
%Lemma~\ref{lem:sdelta},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\frac{\MinProb}{2\TieDensity}$ is at most $\frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) < \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}

>>>>

\begin{rlemma}{Lemma}{\ref{lem:no-incentives}}
Fix an arm $i$.
Let $s \geq \exp(2/\MinProb)$, and let $\tau_s$ be the (random)
time when arm $i$ is pulled for the \Kth{s} time.
Let $\hat{x} = \frac{1}{2\Diam d}
  \cdot \min(\TieCutoff, \frac{\MinProb}{2\TieDensity})$.
Under \AccEU{\tau_s}{\hat{x}},
this pull of arm $i$ is not incentivized.
\end{rlemma}

\begin{proof}
By Lemma~\ref{lem:right-choice},
under the event \AccEU{\tau_s}{\hat{x}},
all agent types \AgV with
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}})
> 2\Diam d \hat{x}$
will pull their best arm \Best{\AgV}.
Notice that $2\Diam d \hat{x}
= \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$

By Assmption~\ref{A1},
the measure of agents (across all arms)
whose best and second-best arm differ in utility by less
than $\min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})$
is at most
$\TieDensity \cdot \min(\TieCutoff, \frac{\MinProb}{2 \TieDensity})
\leq \frac{\MinProb}{2}$.
In particular, this bound holds for agents whose best arm is $i$.
By Assumption~\ref{A3}, at least a measure \MinProb of agents has $i$
as their best arm, and thus, at least a measure $\frac{\MinProb}{2}$
will myopically pull arm $i$.
Because $1/\log(s) \pfedit{\le} \frac{\MinProb}{2}$ for
$s \geq \exp(2/\MinProb)$, arm $i$ is not payment-eligible at time
$\tau_s$.
\end{proof}
